### 2019-12-15 article.tex
Experiments and results section started, mean accuracies table added

\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{caption}
%\usepackage{mathpazo}

@@

Without a doubt, fMRI scans are nothing but spatial and temporal connectivities. As we aim to focus on spatial relations and put temporal ones aside, our algorithm must try to keep all of that information in calculations. Besides, Sarraf and Tofighi's method loses a lot of these connectivities by flattening data toward the $z$ axis. In addition to that, the mentioned data conversion will increase our model complexity and variance, especially in a case like Parkinson's disease dataset. In fact, by resizing 198 slices of $39 \times 64 \times 64$ voxels to a 2D $2496 \times 12672$ pixels, we are adding a lot of unnecessarily and incorrect spatial connectivities based on the $t$ axis and losing some important ones in the $z$ axis by misplacing them. As a result, it is predictable that flattening algorithm may lead to overfitting and compute-intensive calculations which can be seen in Figure \ref{fig:SarrafParkinsonTestResult}. This experiment ran on an NVIDIA GTX1080 and took $6h \; 47m \; 36s$.

@@

>>>>

\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{siunitx}
%\usepackage{mathpazo}

@@

Without a doubt, fMRI scans are nothing but spatial and temporal connectivities. As we aim to focus on spatial relations and put temporal ones aside, our algorithm must try to keep all of that information in calculations. Besides, Sarraf and Tofighi's method loses a lot of these connectivities by flattening data toward the $z$ axis. In addition to that, the mentioned data conversion will increase our model complexity and variance, especially in a case like Parkinson's disease dataset. In fact, by resizing 198 slices of $39 \times 64 \times 64$ voxels to a 2D $2496 \times 12672$ pixels, we are adding a lot of unnecessarily and incorrect spatial connectivities based on the $t$ axis and losing some important ones in the $z$ axis by misplacing them. As a result, it is predictable that flattening algorithm may lead to overfitting and compute-intensive calculations which can be seen in Figure \ref{fig:SarrafParkinsonTestResult}. This experiment ran on an NVIDIA\textsuperscript{\tiny\textregistered} GTX1080 and took $6h \; 47m \; 36s$.

@@

\section{Experiments and results}
\label{section:results}
As discussed in Section \ref{section:proposedMethod}, our method does not demand high processing power so we can use a CPU for our experiments. All of the tests had been run on an Intel\textsuperscript{\tiny\textregistered} 4710HQ CPU. Averagely, the training phase takes $1h \; 12m \; 4s$ and the test phase finishes in $6m \; 41s$. Also it worth mentioning that the application consumes 270 megabytes of RAM thanks to the TFRECORD file format.

\begin{table}
	\label{table:averageAccuracies}
	\caption{Average accuracies for different tests}
	\begin{tabular}{ c | c | c }
		\hline
		$i$ & $\overline{C_{i,t}}\;(\%)$ & $\overline{C_i}\;(\%)$ \\ 
		test no. & mean time-slice accuracy & mean accuracy \\ \hline
		1 & 100 & 100 \\
		2 & 97.90 & 100 \\
		3 & 74.83 & 83.33 \\
		4 & 96.30 & 100 \\
		5 & 97.14 & 100 \\
		6 & 100 & 100 \\
		7 & 98.65 & 100 \\
		8 & 78.87 & 83.33 \\
	\end{tabular}
\end{table}
